%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Vitae Resume/CV
%
% Author:
% Carlton Stedman (carlton.stedman@gmail.com)
% https://github.com/carltonstedman/vitae
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
% Based on:
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.2 (3/5/15)
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Add 'print' as an option in square brackets to remove colors for printing
\documentclass[]{vitae-cv}

\begin{document}

\header{Carlton}{Stedman}{
  senior automation engineer}{continuous delivery advocate}{coffee addict}

%------------------------------------------------------------------------------
%	SIDEBAR SECTION
%------------------------------------------------------------------------------

% In the aside, each new line forces a line break
\begin{aside}
\section{contact}
Nashua, NH
~
(401) 36-LIBRE
~
\href{mailto:carlton.stedman@gmail.com}{carlton.stedman@gmail.com}
\href{http://github.com/carltonstedman}{github.com/carltonstedman}
\href{http://twitter.com/carltonstedman}{@carltonstedman}
\section{coding skills}
\textbf{expert}
Bash, Python, Ruby
Chef, Git, Jenkins, Rspec
Make, Packer, Vagrant
{\color{red} $\varheartsuit$}Linux
BDD/TDD, CI/CD
~
\textbf{adept}
{\color{red} $\varheartsuit$}Clojure, \LaTeX, C, JVM
AWS, KVM, Terraform
{\color{red} $\varheartsuit$}FP, OOP
~
\textbf{apprentice}
Ansible, Consul, Docker
Golang, Haskell, JS, R
\end{aside}

%------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%------------------------------------------------------------------------------

\section{experience}

\begin{entrylist}

%------------------------------------------------

\entry
{2013--Now}
{Dyn}
{Manchester, NH}
{\emph{Senior Automation Engineer} \\
Design, develop, maintain, assist, train, and mentor on all aspects of automation, config management, and CI/CD pipeline, including automated provisioning/deployment in dev VMs, AWS integration environments, and releasing to production on metal/KVM. \\

\subsection{technical}
\begin{itemize}
\item Design, test, write, review, document, and deploy Chef cookbooks.
\item Continuously improve internal tools in Python, Ruby, Bash, and Golang.
\item Build Continuous Delivery (CD) pipelines with Chef, Jenkins, Packer, and Git.
\item Develop automated testing with RSpec, Vagrant, Jenkins, and AWS.
\item Maintain and debug Chef Enterprise, Jenkins, and Github
  Enterprise servers.
\end{itemize}

\subsection{leadership}
\begin{itemize}
\item Directly mentor associate-level automation engineers.
\item Perform training and office hours for tools, testing, Chef, CI/CD, and Git.
\item Created and facilitated Continuous Delivery and Ruby bookclubs.
\end{itemize}}

%------------------------------------------------

\entry
{2010--2013}
{Texas Instruments}
{Manchester, NH}
{\emph{Systems Engineer} \\
Defined, modeled, simulated, evaluated, and characterized dc-dc switched-mode power supply (SMPS) integrated circuits (ICs) for telecom, test automation, and merchant power.
\begin{itemize}
\item Focused on PMBus analog and digital multiphase controllers/drivers.
\item Visited, trained, and worked with customers to deliver solutions and drive NPD.
\item Automated power supply IC characterization and testing using LabView/Python.
\end{itemize}}

%------------------------------------------------

\entry
{2007-2010}
{ON Semiconductor}
{East Greenwich, RI}
{\emph{Application Engineer} \\
Defined, modeled, simulated, evaluated, and characterized automotive-grade dc-dc switched-mode power supply (SMPS) integrated circuits (IC).
\begin{itemize}
\item Designed and performed presentations for sales/field and customers.
\item Built Excel-/MathCAD-based design tools, VHDL-AMS/PSPICE models of SMPS.
\item Created evaluation automation hardware and software (Python) system.
\end{itemize}}

%------------------------------------------------

\end{entrylist}

%------------------------------------------------------------------------------
%	EDUCATION SECTION
%------------------------------------------------------------------------------

\section{education}

\begin{entrylist}

%------------------------------------------------

\entry
{2014--Now}
{Certificate {\normalfont in Data Science}}
{John Hopkins University (Coursera)}
{Have completed and verified three courses in Data Science track,
  including:
\begin{itemize}
\item Data Scientist's Toolbox, R Programming, and Exploratory Data
  Analysis.
\end{itemize}}

\entry
{2003--2007}
{Bachelor of Science {\normalfont in Electrical \& Computer Engineering}}
{Worcester Polytechnic Institute}
{\emph{Completed coursework for Minor in Computer Science,
  Overall GPA: 3.41}
\begin{itemize}
\item Triple concentration: analog microelectronics, digital design, and power electronics
\item Algorithms, Assembly, Networking, Operating Systems, Software Design
\end{itemize}}
%------------------------------------------------

\end{entrylist}

%------------------------------------------------------------------------------
%	INTERESTS SECTION
%------------------------------------------------------------------------------

\section{interests}

\textbf{professional} -- automation, continuous delivery, concurrency
\& parallelism, data science, \emph{kaizen}, functional programming, mentorship, programming languages,
tool design \& improvement \\
\textbf{personal} -- coffee homeroasting, cooking, electronics, homebrewing,
powerlifting, yoga

\rule{\linewidth}{.25pt}

\small{This resume written in Xe\LaTeX using Emacs via \href{
    https://github.com/carltonstedman/vitae/releases/tag/1.0.1}{
    github.com/carltonstedman/vitae/releases/tag/1.0.1}}

\end{document}
